-- Problem 1
use joins;
Table employees

1. Find Employees Without a Manager
Tables:
employees(emp_id, emp_name, manager_id)
Problem:
Get the names of employees who do not have a manager 
(i.e., manager_id is NULL or doesn't match any emp_id).


2. Self Join to Get Employee & Their Manager Names
Tables:
employees(emp_id, emp_name, manager_id)

------------------------------------------------

--p2_solution.sql
use db_joins & Tables employees
Problem:
Get a list of employees along with their manager names (use self join).

--------------------------------------------------

--p3_solution.sql
use db_joins & Tables customers , orders

List Customers with No Orders
Tables:
customers(customer_id, name)
orders(order_id, customer_id, order_date)
Problem:
Fetch all customer names who haven’t placed any order.

--------------------------------------------------------

--p4_solution.sql
use db_join and Tables customers & orders;

Country with Maximum Orders
Tables:
orders(order_id, customer_id)
customers(customer_id, country)

Problem:
Find the country that placed the maximum number of orders using joins and GROUP BY.

------------------------------------------------------------------

--p5_solution.sql
use db_joins and Tables  customers & orders;

Latest Order per Customer
Tables:
orders(order_id, customer_id, order_date)

Problem:
Fetch the most recent order for every customer.

-------------------------------------------------------------------------

--p6_solution.sql
use db_joins and tables employees, departments

Get Highest Salary in Each Department
Tables:
employees(emp_id, name, salary, dept_id)
departments(dept_id, dept_name)

Problem:
List the name of each department and the employee with the highest salary in it.

----------------------------------------------------------------------------

--p7_solution.sql
use db_joins tables employees and departments

Department with More Than 1Employees
Tables:
employees(emp_id, dept_id)
departments(dept_id, dept_name)
Problem:
List departments that have more than one  employees.

------------------------------------------------------------------------

--p8_solution.sql
use db_joins and tables products,sales

Products Never Sold
Tables:
products(product_id, product_name)
sales(sale_id, product_id, quantity)Problem:
Problem:
List all products that were never sold.

-------------------------------------------------------------------

--p9_solution.sql
use db_joins and tables product,sales

Find Top 3 Products by Sales
Tables:
products(product_id, product_name)
sales(sale_id, product_id, quantity)

Problem:
Get top 3 products based on total quantity sold, including their names.
